\subsection{Execution Flow}

While designing the MapReduce model for the server-browser architecuture, we compromise for some additional steps (\emph{configuration}, \emph{signal} and \emph{collect}) and efforts (in \emph{split}, \emph{shuffle} and \emph{reduce}) to the original model due to some constraints of our architecture.

\begin{enumerate}

\item \emph{Configuration}. The server records the clients currently registered and lock the incoming registeration during the MapReduce program executes. Clients are put into a client pool in convenience of being used by the following steps. Here we let M be the number of clients in the pool.

\item \emph{Split}. Master server reads and splits the input data. By default, the data is not split by the server; instead it is user's responsibility to split data into multiple files and put them into the input directory. Here we let F be the number of input files.

\item \emph{Dispatch}. Master server dispatch F files to M clients, as well as the map functions and reduce functions. To armotize the number of files received by each client, the ratio r = ceil(F / M) is applied to each client so that they all receive r files in average.

\item \emph{Map}. The map functions take individual chunk as input, and output a set of key-value data corresponding to the chunk. Since we are using javascript the key-value data can be easy represented as a javascript object or a JSON.

\item \emph{Shuffle}. Clients return the map results via Socket.io, and master server immediately send each key-value pair data to different clients. For each intermediate key we assign a reducer that is responsible to reduce the key; in order to do this, we use a mechanism similar to bucketing, and will be described in the next section.

\item \emph{Reduce}. Upon receiving key-value data, clients run the reduce function to sum up values of the key. The data does not come at the same time so the reducer will wait for a signal referring to the end of the execution.

\item \emph{Signal}. When master receives and re-dispatches all data from every map functions, it sends \emph{MAP_ALL_END} signal to all clients, telling them there is no further inputs and thus reducers can upload the result.

\item \emph{Collect}. After the client sends the final key-value result back to master server, the data will be written to the output directory. A brief summary will be shown indicating execution time, number of keys, number of clients, etc.

\end{enumerate}
